Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
comment on the lack of precision on the description of SOL
A bubble plot of number of notes per instrument (x axis) and playing technique (y axis) would be extremely useful
histograms should be half width

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/nbc.png}
\caption{Histogram of the number of groups.}
\label{fig:xp2nbGroup}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/sbc.png}
\caption{Histogram of the size of groups.}
\label{fig:xp2sizeGroup}
\end{figure}

@@

>>>>

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/nbc.png}
\caption{Histogram of the number of groups.
\vl{The width of this figure should be a half page instead of a full page. Pair with next figure. @figure}}
\label{fig:xp2nbGroup}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/sbc.png}
\caption{Histogram of the size of groups.
\vl{The width of this figure should be a half page instead of a full page. Pair with previous figure. @figure}}
\label{fig:xp2sizeGroup}
\end{figure}

@@

\vl{This section is not precise enough in terms of intensity ranges and pitch ranges.
The abbreviations can be removed. @data @writing}

\vl{A bubble plot of number of notes per instrument (x axis) and playing technique
(y axis) would be extremely useful. @data @figure}
